---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# acadyr

<!-- badges: start -->

<!-- badges: end -->

acadyr provides utility functions for creating and working with financial and
academic years in R:

```{r}
library(acadyr)
library(dplyr, warn.conflicts = FALSE)
library(ggplot2)

revenue <- tibble(
  date = seq.Date(as.Date("2020-01-01"), as.Date("2022-01-01"), by = "3 months"),
  financial_year = financial_year(date),
  academic_year = academic_year(date),
  revenue = rnorm(9, 10000, 1000)
)

revenue
```

These data types also play nicely with ggplot2:
```{r}
revenue |> 
  ggplot(aes(financial_year, revenue)) +
  geom_bar(stat = "summary", fun = "sum") +
  labs(
    title = "Revenue by Financial Year",
    subtitle = "X-axis labels are nicely formatted by default"
  )
```

## Installation
acadyr is not yet on CRAN but you can install it from GitHub using {pak}:
```{r}
#| eval: false

# install.packages("pak")
pak::pak("wurli/acadyr")
```


## Motivation?

Non-calendar year types can cause headaches in everyday analysis for
several reasons:

-   They (usually) don't begin on January 1st, meaning they don't
    integrate easily with other date classes

-   Formatting for display is a pain

-   Different use cases may require financial/academic years to roll over on
    different times. For example, the UK financial year begins on April 1st,
    but the Australian financial year begins on July 1st

## Acknowledgements

-   This package is powered by {vctrs}, and its creation was largely
    informed by the (excellent) accompanying documentation
